Btech Project - Progress Diary

### 2017-09-06 Work_report/Daily_progress/work_progress_daily.tex
Commit from the new computer Hue hue

\subsubsection{July 29 : Saturday}

@@

\end{document}

>>>>

\subsubsection{July 29 : Saturday}
Probably no work done

\section{Week}
\subsection{Sept 6 : Thursday}
Discussion with the prof. Main points noted below. Also has what all needs to be done before tomorrow's meeting.
\begin{itemize}
\item Graph Signal. Needs a more concrete definition. Can the vectors be of different dimensions? (I think not, but need to verify this.)
\item An image may have 100-200 superpixels, which is not a constant. So can't use the same graph for all of them. Can we exploit the graph structure? GCN though requires the same graph structure to be followed, otherwise it won't be able to exploit the weights and would essentially require new training and generally useless.
\item We would also like to encode the spatial connections of the superpixels.
\item When we have arbitrary shape, we don't want to have any kind of orientation information, may mess things up.
\end{itemize}

@@

\end{document}\grid
